---
title: "Data Science"
format: html
editor: visual
---

# What do you think being a data scientist is about?

A data scientist's goal is to determine the narrative of a data set and using that information in creating ways to meet the needs of a client.

# What differences/similarities do you see between data scientists and statisticians?

Both disciplines require a background in statistics, computer science, and analytical thinking. What they do with this background is where they differ. In a way, the statistician stops at the modeling and analysis of a data set. The data scientist takes the information gained from the analysis and applies it to determine a solution that meets the needs of their client.

# How do you view yourself in relation to these two areas?

I view myself as a rather novice data scientist more than I would consider myself a statistician. I enjoy determining the story a set of data is telling, but I want to apply that information to create solutions to problems, such as workplace process efficiency.

# Iris

## Create an R code chunk to determine the class, type, and structure of the object y

```{r}
y <- density(iris$Sepal.Length)
```

```{r}
class(y)
typeof(y)
str(y)
```

## Create an R code chunk that uses the plot funciton on y.

```{r}
#| echo: false
plot(y)
```
