---
title: "Data Science"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Questions and Answers
## What do you think being a data scientist is about?

Data scientists structure data for use in analysis, then conduct the data analysis and provide a client with information required to solve a problem, like improving process or cost effectiveness or improving sales. 
   

## What differences/similarities do you see between data scientists and statisticians?

Both disciplines require a background in statistics, computer science, and analytical thinking. What each discipline does with this background is where they differ. In a way, the statistician stops at the modeling and analysis of a data set while the data scientist uses the information gained from an analysis and applies it to determining a solution to a problem.

## How do you view yourself in relation to these two areas?

I would consider myself a rather novice data scientist more than I would say I'm a statistician. I enjoy determining the story a set of data is telling, but I want to apply that information to create solutions to problems, such as workplace process efficiency.

# Iris Data


## Create an R code chunk to determine the class, type, and structure of the object y

```{r}
#| echo: false
y <- density(iris$Sepal.Length)
```

```{r}
#| echo: false
class(y)
typeof(y)
str(y)
```

## Create an R code chunk that uses the plot funciton on y.

```{r}
#| echo: false
plot(y)
```
